---
title: "How do Torontonians percieve Climate Change"
subtitle: "Analysing survey from OpenDataToronto"
author: 
  - Aamishi Avarsekar
thanks: "Code and data are available at: https://github.com/aamishi/TorontoniansCombatClimateChange"
date: today
date-format: long
format: pdf
number-sections: true
bibliography: references.bib
---

```{r, echo=FALSE}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```


# Introduction

This paper investigates the areas of improvement that the Citizens of Toronto seek for within the city. Pointedly, it studies the demographic difference of different ages and social groups and their inclination towards funding or defunding Toronto’s future.

The data for this paper is sourced from Open Data Toronto (@opendatatoronto) and is downloaded, cleaned and analyzed using the R Programming language (@citeR).

Aspects of this paper were written using the LLM ChatGPT 3.5 and 4.0.


# Data {#sec-mydatasection}

```{r, echo=FALSE}
#| echo: false
analysis_data <- read_csv("../data/analysis_data/analysis_data_demo.csv", show_col_types = FALSE)

# demographs for defunding
# Step 1: Summarize to get total counts for DecreaseFunding (ignoring age for now)
top_decrease_funding <- analysis_data %>%
  group_by(DecreaseFunding) %>%
  summarise(total_count = n(), .groups = 'drop') %>%
  arrange(desc(total_count)) %>%
  top_n(5, wt = total_count) %>%
  pull(DecreaseFunding)

# Step 2: Now group by DecreaseFunding and age, and filter for the top 5 bins
data_summary <- analysis_data %>%
  filter(DecreaseFunding %in% top_decrease_funding) %>%  # Filter for only top 5 bins
  group_by(DecreaseFunding, Age) %>%
  summarise(count = n(), .groups = 'drop') %>%
  arrange(desc(count))

# Step 3: Create the bar plot for the top 5 bins, facet by age
ggplot(data_summary, aes(x = reorder(DecreaseFunding, -count), y = count, fill = Age)) +
  geom_bar(stat = "identity", position = "stack", color = "black") +  # Or 'stack' for stacked bars
  labs(title = "Top 5 DecreaseFunding Bins with Age Information", x = "DecreaseFunding", y = "Count") +
  theme_minimal()


```


# Results

```{r}

```

```{r}

```




# Discussion


\newpage

\appendix

# Appendix {-}


# Additional data details

## Diagnostics

```{r}

```



\newpage


# References


